\documentclass[a4paper, 11pt]{article}
\usepackage[margin=0.5in]{geometry}
\begin{document}
\raggedright
\textbf{Yash Mahajan}\\
Department of Computer Science and Engineering\\
Indian Institute of Technology Kanpur, India\\
\textit{Email: ymahajan@iitk.ac.in}\\~\\
\hrule
\vspace{0.33em}
\hrule
~\\
People find me to be an upbeat, self-motivated team player with excellent communication skills. For the past several years I have worked in lead qualification, telemarketing, and customer service in the technology industry. My experience includes successfully calling people in director-level positions of technology departments and developing viable leads. I have a track record of maintaining a consistent call and activity volume and consistently achieving the top 10 percent in sales, and I can do the same thing for your company.
\vspace{0.33em}
~\\
\hrule
\vspace{0.33em}
\hrule
~\\
\textbf{Education}\\~\\

\begin{tabular}{ |c|c|c|c|} 
 \hline
 Matriculation & 2014 & NDPS Indore & 10 CGPA\\ \hline
 Intermediate & 2016 &Annie Besant School Indore &  100\%\\ 
 \hline
B.Tech. & 2016-Present & Indian Institute of Technology Kanpur &  10/10 CPI \\ 
 \hline
\end{tabular}\\~\\~\\
\textbf{Course Details-}\\~\\
\begin{tabular}{ |c|c|c|} 
 \hline
 \textbf{Semester Details} & \textbf{Total Credits} &  \textbf{Highlights}\\ \hline
 Aug 2016-Dec 2016 & 53 &  PE101\\ 
 \hline
Jan 2017-April 2017 & 51 & PE102\\ 
 \hline
  Aug 2017-Dec 2017 & 61 &  TA201\\ 
 \hline
\end{tabular}\\~\\~\\
\textbf{Skills}\\~\\
-Computer Science       : Operating systems, Machine learning\\
-Programming languages  : C, C++, Java, Scripting languages (bash, awk)\\~\\
\textbf{Projects}\\
\begin{enumerate}
\item \textbf{Unsupervised Video Surveillance} \hfill\textit{(May 2017-Dec 2017)}\\
This project involved the development of a novel technique to detect unusual activities in videos in an
unsupervised manner.  We used pLSA with an appropriate choice for features on video clips to obtain
clustering of similar videos, and any new activity different from the ones learned was flagged as unusual.
We also extended the idea to multi person unusual activity detection.
\item \textbf{Improving Performance with MKL in SVMs} \hfill\textit{(May 2017-Dec 2017)}\\
Support Vector Machines learn linear classifiers from labelled training data to predict labels for previously unseen test data.  Kernels with SVM’s allow to learn non linear classifiers, and hence lead to much
higher classification accuracy's in practice.  We are learning
non linear kernel combinations
to give
us even better classification accuracy's and are seeing a possibility of a significant performance increase.
\end{enumerate}
\textbf{Awards and Achievements}\\
\begin{itemize}
\item[--] Rank 1 in IIT-JEE 2016
\item[--] Gold medalist in International Informatics Olympiad 2015.
\end{itemize}
\textbf{Hobbies}\\
\begin{itemize}
\item[--] Sports   : Cricket,Football
\item[--] Music    : Synthesizer,Flute,Piano
\item[--] -Others  : Video Games,Movies
\end{itemize}
\end{document}

